The Heavy Photon Search Test Detector

### 2013-11-19 hps-testrun-nim.tex
Adding text on momentum resolution and scale

By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair production 
kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the 
top and one in the bottom half of the SVT, with momentum larger than 400~MeV were selected. 
The pair production 
kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the 
invariant mass and ratio of electron momentum over the sum of electron and positron. 
 \begin{center}
{\small
\begin{figure*}[ht]
   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
%   \includegraphics[scale=0.25]{test2012/vertexing/figures/h_ratioEsum_h_ratioEsum_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair.}
\label{fig:pair_kin}
\end{figure*}
}
\end{center}

For the vertexing 
performance the foremost difference compared to electron beam running is that the target was 
located approximately 67~cm from our nominal target position; giving almost collinear tracks in the detector. 
This degrades the vertex resolution along the 
beam line compared to that expected in an electron beam with tracks from the nominal target position. 
Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
in the test run. Nevertheless, useful information can still be 
obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
approach of the momentum vectors extrapolated in the 
upstream direction from our analyzing magnet, taking into account the measured fringe field of the PS magnet. 
 \begin{center}
{\small
	 \begin{figure*}[ht]
	% Plot info:
	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_trigsel4hit_pair1351_twotrkfilt-v6-paper}
	\includegraphics[width=5cm]{figures/h_vtx_fr_y_h_vtx_y_trigsel4hit_pair1351_twotrkfilt-v6-paper}
	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
	\caption{ Vertex position represented by the distance of 
	closest approach of the extrapolated momentum vectors upstream of the PS magnet taking into account 
	the measured fringe field. The overall shift from zero in the x-direction is 
	due to a 30~mrad rotation of the SVT with respect to the beam line.}
	\label{fig:vtx_pos}
\end{figure*}
}
\end{center}
%While the tails of the vertex distribution expected in electron beam running is not accessible here the 
%fact that the core is relatively well described provides confidence of the description of the amount of 
%material and the model used for simulating multiple scattering in the target.  
%These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex 
%resolution that determine the sensitivity are limited by multiple scattering.

>>>>

By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
production kinematics and in particular those related to our vertex performance. Pairs of opposite charge 
tracks, one in the top and one in the bottom half of the SVT, with momentum larger than 400~MeV were 
selected. The pair production kinematics are relatively well reproduced given the alignment of the 
tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of 
electron and positron. 
 \begin{center}
{\small
\begin{figure*}[ht]
   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
\label{fig:pair_kin}
\end{figure*}
}
\end{center}
We estimate the accuracy of the SVT momentum scale and resolution by looking at the agreement 
between data and simulation in the shape of the kinematic distributions for single- and two track 
events.  By adjusting the overall momentum scale and smearing the simulated events with a 
Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
resolution in the Test run. This uncertainty is

For the vertexing performance the foremost difference compared to electron beam running is that the 
target was located approximately 67~cm from our nominal target position; giving almost collinear tracks 
in the detector. This degrades the vertex resolution along the 
beam line compared to that expected in an electron beam with tracks from the nominal target position. 
Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
in the Test run. Nevertheless, useful information can still be 
obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
approach of the momentum vectors extrapolated in the upstream direction from our analyzing magnet, 
taking into account the measured fringe field of the PS magnet. 
 \begin{center}
{\small
	 \begin{figure*}[ht]
	% Plot info:
	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_trigsel4hit_pair1351_twotrkfilt-v6-paper}
	\includegraphics[width=5cm]{figures/h_vtx_fr_y_h_vtx_y_trigsel4hit_pair1351_twotrkfilt-v6-paper}
	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
	\caption{ Vertex position represented by the distance of closest approach of the extrapolated 
	momentum vectors upstream of the PS magnet taking into account the measured fringe field. The 
	overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to the 
	beam line.}
	\label{fig:vtx_pos}
\end{figure*}
}
\end{center}
%While the tails of the vertex distribution expected in electron beam running is not accessible here the 
%fact that the core is relatively well described provides confidence of the description of the amount of 
%material and the model used for simulating multiple scattering in the target.  
%These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex 
%resolution that determine the sensitivity are limited by multiple scattering.
